---
title: "Computational Genomics with R"
output: html_notebook
---
```{r}
library(qvalue)
data(hedenfalk)

qvalues <- qvalue(hedenfalk$p)$q
bonf.pval=p.adjust(hedenfalk$p,method ="bonferroni")
fdr.adj.pval=p.adjust(hedenfalk$p,method ="fdr")

plot(hedenfalk$p,qvalues,pch=19,ylim=c(0,1),
     xlab="raw P-values",ylab="adjusted P-values")
points(hedenfalk$p,bonf.pval,pch=19,col="red")
points(hedenfalk$p,fdr.adj.pval,pch=19,col="blue")
legend("bottomright",legend=c("q-value","FDR (BH)","Bonferroni"),
       fill=c("black","blue","red"))
```
# 3.4.1 How to summarize collection of data points: The idea behind statistical distributions   
1. Calculate the means and variances of the rows of the following simulated data set, and plot the distributions of means and variances using hist() and boxplot() functions. [Difficulty: Beginner/Intermediate]   
```{r, label = problem-1}
set.seed(100)

#sample data matrix from normal distribution
gset=rnorm(600,mean=200,sd=70)
data=matrix(gset,ncol=6)

data_means_row <- apply(data, 1, mean)
data_variances_row <- apply(data, 1, var)
hist(data_means_row)
hist(data_variances_row)
boxplot(data_means_row)
boxplot(data_variances_row)
```
2. Using the data generated above, calculate the standard deviation of the distribution of the means using the sd() function. Compare that to the expected standard error obtained from the central limit theorem keeping in mind the population parameters were σ=70 and n=6. How does the estimate from the random samples change if we simulate more data with `data=matrix(rnorm(6000,mean=200,sd=70),ncol=6)`? [Difficulty: Beginner/Intermediate]   
```{r, label = problem-2}
sd_means_dist <- sd(data_means_row)
print(sd_means_dist)
print(70 / sqrt(6))

data2=matrix(rnorm(6000,mean=200,sd=70),ncol=6)
data2_means_row <- apply(data2, 1, mean)
sd2_means_dist <- sd(data2_means_row)
print(sd2_means_dist)
print("When the n is made 10x bigger, the standard deviation increases by around 0.2.")
```
3. Simulate 30 random variables using the rpois() function. Do this 1000 times and calculate the mean of each sample. Plot the sampling distributions of the means using a histogram. Get the 2.5th and 97.5th percentiles of the distribution. [Difficulty: Beginner/Intermediate]   
```{r, label = problem-3}
means_poisson <- c()
for (n in 1:1000) {
  means_poisson[n] <- mean(rpois(30, 1))
}
hist(means_poisson)
print(quantile(means_poisson, probs = c(0.025, 0.975)))
```
4. Use the t.test() function to calculate confidence intervals of the mean on the first random sample pois1 simulated from the rpois() function below. [Difficulty: Intermediate]
```{r, label = problem-4}
#HINT
set.seed(100)

#sample 30 values from poisson dist with lamda paramater =30
pois1=rpois(30,lambda=5)

my_ttest <- t.test(pois1, alternative = "t", mu = 5)
my_ttest
```

