---
title: "Computational Genomics with R"
output: html_notebook
---
```{r}
library(qvalue)
data(hedenfalk)

qvalues <- qvalue(hedenfalk$p)$q
bonf.pval=p.adjust(hedenfalk$p,method ="bonferroni")
fdr.adj.pval=p.adjust(hedenfalk$p,method ="fdr")

plot(hedenfalk$p,qvalues,pch=19,ylim=c(0,1),
     xlab="raw P-values",ylab="adjusted P-values")
points(hedenfalk$p,bonf.pval,pch=19,col="red")
points(hedenfalk$p,fdr.adj.pval,pch=19,col="blue")
legend("bottomright",legend=c("q-value","FDR (BH)","Bonferroni"),
       fill=c("black","blue","red"))
```
# 3.4.1 How to summarize collection of data points: The idea behind statistical distributions   
1. Calculate the means and variances of the rows of the following simulated data set, and plot the distributions of means and variances using hist() and boxplot() functions. [Difficulty: Beginner/Intermediate]   
```{r, label = problem-1}
set.seed(100)

#sample data matrix from normal distribution
gset=rnorm(600,mean=200,sd=70)
data=matrix(gset,ncol=6)

data_means_row <- apply(data, 1, mean)
data_variances_row <- apply(data, 1, var)
hist(data_means_row)
hist(data_variances_row)
boxplot(data_means_row)
boxplot(data_variances_row)
```
2. Using the data generated above, calculate the standard deviation of the distribution of the means using the sd() function. Compare that to the expected standard error obtained from the central limit theorem keeping in mind the population parameters were σ=70 and n=6. How does the estimate from the random samples change if we simulate more data with `data=matrix(rnorm(6000,mean=200,sd=70),ncol=6)`? [Difficulty: Beginner/Intermediate]   
```{r, label = problem-2}

```

